Title
========================================================
Pulling the health facility match up result and define the "Best" LGAs

Step1: preparing raw data from Json files
-----------------------------------------
```{r, echo=TRUE, eval=TRUE, message=FALSE}
# Loading matching status data from nmis dump
require(RJSONIO)
require(plyr)
require(ggplot2)

# pulling Myf's matching data 
baseline_status <- fromJSON("~/Dropbox/Nigeria/Nigeria 661 Baseline Data Cleaning/in_process_data/mop_up_matching_result/Matching status/nmis_by_lga.json", simplifyWithNames=T)

# call rbind.fill on list of dfs
baseline_status <- do.call("rbind.fill", lapply(baseline_status, as.data.frame, stringsAsFactors=F))

baseline_status <- subset(baseline_status, select=c("lga_id", "health_total", "health_finished", "health_matched"))
baseline_status <- rename(baseline_status, 
                          c("health_total" = "baseline_total",
                            "health_matched" = "matched",
                            "health_finished" = "baseline_finished"))


facility_status <- fromJSON("~/Dropbox/Nigeria/Nigeria 661 Baseline Data Cleaning/in_process_data/mop_up_matching_result/Matching status/lga_by_lga.json", simplifyWithNames=T)

facility_status <- do.call("rbind.fill", lapply(facility_status, as.data.frame, stringsAsFactors=F))

facility_status <- subset(facility_status, select=c("lga_id", "health_total", "health_finished"))
facility_status <- rename(facility_status, 
                          c("health_total" = "facility_total",
                            "health_finished" = "facility_finished"))

```
Step2: combine data from all sources
-------------------------------------
* Joined baseline & facility data
* define coverage error by facility/baseline < 0.7 or NA or Inf in the ratio
```{r}
# Load lga info
lgas <- read.csv("~/Dropbox/Nigeria/Nigeria 661 Baseline Data Cleaning/lgas.csv", stringsAsFactors=F)

health <- merge(lgas, baseline_status, by="lga_id", all=T)
health <- merge(health, facility_status, by="lga_id", all=T)
health$error <- (health$facility_total/health$baseline_total < 0.7 | 
              is.infinite(health$facility_total/health$baseline_total) | 
              is.na(health$facility_total/health$baseline_total))
summary(health$facility_total)
summary(health$baseline_total)
summary(health$error)
```

Step 3: Aggregate and get the state level
```{r}
health_state <- ddply(health, .(state), summarize,
             match_count = sum(matched, na.rm=T),
             baseline_total = sum(baseline_total, na.rm=T),
             baseline_finished = sum(baseline_finished, na.rm=T),
             facility_total = sum(facility_total, na.rm=T),
             facility_finished = sum(facility_finished, na.rm=T),
             coverage_error = sum(error)
              )

health_state$base_facil <- health_state$baseline_total/health_state$facility_total
health_state$match_facil <- health_state$match_count/health_state$facility_total
health_state$facil_complete <- health_state$facility_finished/health_state$facility_total
health_state$base_complete <- health_state$baseline_finished/health_state$baseline_total
health_state$match_base <- health_state$match_count/health_state$baseline_total
health_state$facil_base <- health_state$facility_total/health_state$baseline_total
health_state$total_non_match_vs_facil <- (health_state$facility_total + health_state$baseline_total - 2*health_state$match_count)/health_state$facility_total

health_state$idx <- health_state$base_facil + health_state$match_facil + health_state$facil_complete

range01 <- function(x){(x-min(x))/(max(x)-min(x))}
health_state$std_error_cov <- range01(health_state$coverage_error)

health_state$idx2 <- (0.7*order(health_state$match_facil, decreasing=F) + 
                   0.4*order(health_state$facil_base, decreasing=T) +
                    0.3*order(health_state$total_non_match_vs_facil, decreasing=T))
health_state$idx2_adj <- health_state$idx2 - health_state$std_error_cov * quantile(health_state$idx2, probs=0.5) 


health_state <- arrange(health_state, desc(idx2_adj))
```








#####
ggplot(health, aes(baseline_total, facility_total)) + geom_point() +
  ylim(0, 300) + xlim(0, 300) +
  geom_abline(intercept = 0, slope = 1) + 
  geom_abline(intercept = 0, slope = 0.7, color = "red") 

```
